A Survey of Exoskeleton Control (Draft 1.1)

### 2015-09-20 paper.tex
more updates

\begin{verbatim}
07139975
2015 IEEE International Conference on Robotics and Automation (ICRA)
Towards Balance Recovery Control for Lower Body Exoskeleton Robots
with Variable Stiffness Actuators: Spring-Loaded Flywheel Model
Corinne Doppmann, Barkan Ugurlu, Masashi Hamaya, Tatsuya Teramae,
Tomoyuki Noda, and Jun Morimoto
\end{verbatim}

@@

step-width adaptation algorithm

>>>>

\begin{verbatim}
07139975, 07131568
2015 IEEE International Conference on Robotics and Automation (ICRA)
Towards Balance Recovery Control for Lower Body Exoskeleton Robots
with Variable Stiffness Actuators: Spring-Loaded Flywheel Model
Corinne Doppmann, Barkan Ugurlu, Masashi Hamaya, Tatsuya Teramae,
Tomoyuki Noda, and Jun Morimoto
\end{verbatim}

@@

central pattern generator

iterative learning control to acquire $\vtau_{ff}(t)$ for desired trajectories.
